Tracing the Hercules stream around the Galaxy

### 2010-06-01 tex/hercules.tex
groups-simulations: not a Letter anymore

In this Letter I propose that a robust and unambiguous test of the
bar-resonance model for the Hercules stream is a search for the
distinct pattern it predicts as we trace the velocity distribution of
stars near the Solar radius around the Galaxy. \Gaia\ is in a good
position to have the final word on this, but I also show that the
Hercules feature can be detected in the line-of-sight velocity
distribution in selected directions on the sky. Clear signatures are
predicted to be detectable in regions a few kiloparsec from the Sun,
allowing for a clean verification of the bar-resonance model for the
Hercules stream.

>>>>

Here I propose that a robust and unambiguous test of the bar-resonance
model for the Hercules stream is a search for the distinct pattern it
predicts as we trace the velocity distribution of stars near the Solar
radius around the Galaxy. \Gaia\ is in a good position to have the
final word on this, but I also show that the Hercules feature can be
detected in the line-of-sight velocity distribution in selected
directions on the sky. Clear signatures are predicted to be detectable
in regions a few kiloparsec from the Sun, allowing for a clean
verification of the bar-resonance model for the Hercules stream.
